Binocular integration of chromatic and luminance signals

### 2024-03-24 manuscript.Rmd
Fixed Stan model!

processdata <- 2
# the processdata flag has three settings:
# 0: do no analysis, just produce the pdf of the manuscript
# 1: fit psychometric functions and plot graphs
# 2: do Stan modelling (takes N hours)

nsamples <- 100000    # number of Stan samples for modelling
ntotalsimplexfits <- 100    # number of random starting vectors for simplex fits
ncores <- 8    # number of processor cores to use on the host machine
postsampleres <- 400    # resolution of psignifit posterior sampling

# other Stan settings
adaptSteps = 5000  # Number of steps to "tune" the samplers
burnInSteps = 5000
thinSteps <- 10
nChains = 64

# reasonably compact code to check which packages are installed, install the missing ones, and activate all
packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','doParallel','R.matlab','bayestestR','alphahull') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

# helper function to make colours transparent
addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}

@@

p <- 10^p
p[2] <- p[2] + 1
p[2] <- min(p[2],10)
p[1] <- 1 + p[1] + p[2]
p[3] <- 1 + p[3]

@@

use_miniconda('r-reticulate')
# install psignifit in the terminal with:
# sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
ps <- import('psignifit')

# calculate constant to scale the slope parameter to the Gaussian SD
C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)

if (!dir.exists('local/fits')){dir.create('local/fits')}

@@

ex1data <- read.csv('local/Experiment1.csv')
ex2data <- read.csv('local/Experiment2.csv')

@@

allthresh[subj,expt,cond,pedlevel] <- res$Fit[1]
allslope[subj,expt,cond,pedlevel] <- 10.3/(res$Fit[2]/C)
}

@@

meanthresh <- apply(allthresh,2:4,mean)
meanslope <- 10^apply(log10(allslope),2:4,mean)

@@

  MCSthresh[subj,cond] <- res$Fit[1]
  MCSslope[subj,cond] <- 10.3/(res$Fit[2]/C)

@@

@@

@@

pedlist <<- seq(-12,30,6)
allp <- matrix(0,nrow=3,ncol=7)
allparams <- array(0,dim=c(3,ntotalsimplexfits,8))
allrms <- NULL
 for (cond in 1:3){
   print(cond)
   datatofit <<- meanthresh[cond,,]

@@

   finalout <- matrix(0,nrow=ntotalsimplexfits,ncol=8)
   for (n in 1:ntotalsimplexfits){
     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){
       load(file=paste0('local/fits/E',cond,'f',n,'.RData'))
       finalout[n,] <- allout
     }
   }
   i <- which(finalout[,1]==min(finalout[,1]))
   p <- 10^finalout[i[1],2:8]
   allrms[cond] <- finalout[i[1],1]
   p[2] <- p[2] + 1
   p[2] <- min(p[2],10)
   p[1] <- 1 + p[1] + p[2]
   p[3] <- 1 + p[3]
   allp[cond,] <- p
   pedlist <<- seq(-6,36,6)

   allparams[cond,,] <- finalout
 }

@@

```{r plotmodellingsimplex, include=FALSE}

@@

pedlist <- -12:39
pedlevelsC <- 10^(pedlist/20)
pedlevelsC[1] <- 0
allpred <- array(0,dim=c(3,4,length(pedlist)))

for (expt in 1:3){
  for (cond in 1:4){
    for (pedlev in 1:length(pedlist)){
      allpred[expt,cond,pedlev] <- discriminate(allp[expt,],pedlevelsC[pedlev],cond)
    }
  }
}
allpreddB <- 20*log10(allpred)

pdf('Figures/dipperssimplex.pdf',width=12,height=5)

@@

par(pty="s",mfcol=c(1,3))  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(a) Achromatic',cex.main=2)

for (cond in 1:4){
  arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]+SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanthresh[1,cond,],pedcontrasts,meanthresh[1,cond,]-SEthresh[1,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
  lines(pedlist,allpreddB[1,cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanthresh[1,cond,],pch=16,col=collist[cond],cex=1.5)
}
text(24,-9,paste0('RMS = ',round(allrms[1],digits=2),'dB'),cex=2)
legend(-12,36,c('Monocular','Binocular','Half-bin','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))  
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(b) Red/Green',cex.main=2)

for (cond in 1:4){
  arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]+SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanthresh[3,cond,],pedcontrasts,meanthresh[3,cond,]-SEthresh[3,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
 # lines(pedcontrasts,meanthresh[3,cond,],col=collist[cond],lwd=2)
  lines(pedlist,allpreddB[3,cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanthresh[3,cond,],pch=16,col=collist[cond],cex=1.5)
}
text(24,-9,paste0('RMS = ',round(allrms[2],digits=2),'dB'),cex=2)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(c) Blue/Yellow',cex.main=2)

for (cond in 1:4){
  arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]+SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanthresh[2,cond,],pedcontrasts,meanthresh[2,cond,]-SEthresh[2,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
 # lines(pedcontrasts,meanthresh[2,cond,],col=collist[cond],lwd=2)
  lines(pedlist,allpreddB[2,cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanthresh[2,cond,],pch=16,col=collist[cond],cex=1.5)
}
text(24,-9,paste0('RMS = ',round(allrms[3],digits=2),'dB'),cex=2)

@@

summation <- meanthresh[,1,1] - meanthresh[,2,1]

@@

```{r domodelling, include=FALSE}

@@

modelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;    
  }
  parameters {
    real<lower=0> p[Ndatasets];
    real<lower=0> q[Ndatasets];    
    real<lower=0> m[Ndatasets];
    real<lower=0> S[Ndatasets];  
    real<lower=0> Z[Ndatasets];
    real<lower=0> w[Ndatasets];
    real<lower=0> k[Ndatasets];

    real<lower=0> sigma ;
    real<lower=0> pmu ; 
    real<lower=0> qmu ; 
    real<lower=0> mmu ;
    real<lower=0> Smu ;
    real<lower=0> Zmu ; 
    real<lower=0> wmu ; 
    real<lower=0> kmu ;

@@

    pmu ~ normal( 1.4 , 1.4/3 ) ;
    qmu ~ normal( 6.59 , 6.59/3 ) ;
    mmu ~ normal( 1.28 , 1.28/3 ) ;
    Smu ~ normal( 0.985 , 0.985/3 ) ;
    Zmu ~ uniform( 0.001 , 100 ) ;
    wmu ~ normal( 1 , 0.3333 ) ;
    kmu ~ normal( 0.194 , 0.194/2 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    msigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Ssigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

@@

    dprime = (targresp-nullresp)/k[s[i]] ;

    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;

    }
  }  
" # close quote for modelString

@@

ex1data <- read.csv('local/Experiment1.csv')
ex1data$Condition <- ceiling(ex1data$Condition/2)

@@

expdata <- data.frame(datasets,experiments,conditions,pedestals,targets,ntrials,ncorrect)

dataList = list(ncorrect = expdata$ncorrect, ntrials = expdata$ntrials, PedestalContrast = expdata$pedestals, TargetContrast = expdata$targets, c = expdata$conditions, s = expdata$datasets, Ndatasets = max(expdata$datasets), Ntotal = nrow(expdata))

@@

  save(file=paste0('local/FullMod.RData'),list=c('stanFit'))

@@

@@

  load(file=paste0('local/FullMod.RData'))

  draws <- extract(stanFit)

  p <- map_estimate(draws$pmu+draws$qmu)
  q <- map_estimate(draws$qmu)
  m <- map_estimate(draws$mmu)
  k <- map_estimate(draws$kmu)
  S <- map_estimate(draws$Smu)
  Z <- map_estimate(draws$Zmu)
  w <- map_estimate(draws$wmu)
  paramvect <- c(p,q,m,S,Z,w,k)

  allsamples <- array(0,dim=c(7,length(plist)))
    allsamples[1,] <- plist
    allsamples[2,] <- qlist
    allsamples[3,] <- mlist
    allsamples[4,] <- Slist
    allsamples[5,] <- Zlist
    allsamples[6,] <- wlist
    allsamples[7,] <- klist

>>>>

processdata <- 0
# the processdata flag has three settings:
# 0: do no analysis, just produce the pdf of the manuscript
# 1: fit psychometric functions and plot graphs
# 2: do Stan modelling and simplex fitting (takes several hours, simplex sometimes gets stuck!)

nsamples <- 100000    # number of Stan samples for modelling
ntotalsimplexfits <- 100    # number of random starting vectors for simplex fits
ncores <- 8    # number of processor cores to use on the host machine
postsampleres <- 200    # resolution of psignifit posterior sampling

# other Stan settings
burnInSteps <- 5000   # Number of steps to "tune" the samplers
thinSteps <- 10
nChains <- 8

# reasonably compact code to check which packages are installed, install the missing ones, and activate all
packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','parallel','doParallel','R.matlab','bayestestR','alphahull','kableExtra') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

# ncores <- parallel::detectCores()  # auto-detect number of cores (optional)

if (processdata>1){
  use_miniconda('r-reticulate')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

```{r subfunctions, include=FALSE}

# helper functions used throughout the manuscript

addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}

@@

p <- 10^p
p[2] <- p[2] + 1
p[2] <- min(p[2],16)
p[1] <- 1 + p[1] + p[2]
p[1] <- min(p[1],20)
p[3] <- 1 + p[3]

@@

return(output)}

make_soft_window <- function(W,H,D=0.9){
  # Mark's function to make sine-wave gratings, ported from Matlab
  # W is width (in pixels), H is height (in pixels)
  # D is the diameter of the soft window at half height as a proportion of the width

```{r checkfordata, include=FALSE}

# check for presence of essential data files and folders locally - download from OSF if missing

if (!dir.exists('local')){dir.create('local')}
if (!dir.exists('local/fits')){dir.create('local/fits')}

osfrepo <- '3vdga'

if (!file.exists('local/Experiment1.csv')){}
if (!file.exists('local/Experiment2.csv')){}
if (!file.exists('local/Experiment3.csv')){}
if (!file.exists('local/fundamentals.csv')){}
if (!file.exists('local/isosettings.csv')){}
if (!file.exists('local/phosphors.csv')){}

if (processdata < 1){
 if (!file.exists('local/thresholddata.RData')){}
 if (!file.exists('local/thresholddataDisc.RData')){}
 if (!file.exists('local/MCSdata.RData')){}
}

if (processdata < 2){
 if (!file.exists('local/simplexfits.RData')){}
 if (!file.exists('local/stanfit1.RData')){}
 if (!file.exists('local/stanfit2.RData')){}
 if (!file.exists('local/stanfit3.RData')){}
 if (!file.exists('local/stanfit4.RData')){}
}

if (!file.exists('references.bib')){}
if (!file.exists('journal-of-vision.csl')){}

@@

ex1data <- read.csv('local/Experiment1.csv')
ex2data <- read.csv('local/Experiment2.csv')
ex3data <- read.csv('local/Experiment3.csv')

@@

allthresh[subj,expt,cond,pedlevel] <- res$Fit[1]
allslope[subj,expt,cond,pedlevel] <- 20*log10(10.3/(res$Fit[2]/C))
}

@@

meanthresh <- apply(allthresh,2:4,mean)
meanslope <- apply(allslope,2:4,mean)

@@

  MCSthresh[subj,cond] <- res$Fit[1]
  MCSslope[subj,cond] <- 20*log10(10.3/(res$Fit[2]/C))

@@

sublist3 <- unique(ex3data$Subject)

allthresh3 <- array(0,dim=c(length(sublist3),4,8))
allslope3 <- array(0,dim=c(length(sublist3),4,8))
for (subj in 1:length(sublist3)){
  subdata <- subset(ex3data,Subject==sublist3[subj])
for (cond in 1:4){
  conddata <- subset(subdata,Condition==(2*cond)|Condition==((2*cond)-1))
  pedlevs <- unique(conddata$PedestalContrast)
for (pedlevel in 1:8){

allthresh3[subj,cond,pedlevel] <- res$Fit[1]
allslope3[subj,cond,pedlevel] <- 20*log10(10.3/(res$Fit[2]/C))
}

}}}

# shift hbin and dich conditions up one
allthresh3[,3,2:8] <- allthresh3[,3,1:7]
allthresh3[,4,2:8] <- allthresh3[,4,1:7]
allslope3[,3,2:8] <- allslope3[,3,1:7]
allslope3[,4,2:8] <- allslope3[,4,1:7]
# duplicate the mon threshold conditions for hbin and dich
allthresh3[,3,1] <- allthresh3[,1,1]
allthresh3[,4,1] <- allthresh3[,1,1]
allslope3[,3,1] <- allslope3[,1,1]
allslope3[,4,1] <- allslope3[,1,1]

meanthresh3 <- apply(allthresh3,2:3,mean)
meanslope3 <- apply(allslope3,2:3,mean)

SEthresh3 <- apply(allthresh3,2:3,sd)/sqrt(length(sublist3))
SEslope3 <- apply(allslope3,2:3,sd)/sqrt(length(sublist3))

save(file='local/thresholddataDisc.RData',list=c('allthresh3','allslope3','meanthresh3','meanslope3','SEthresh3','SEslope3'))

@@

load('local/thresholddata.RData')
load('local/thresholddataDisc.RData')

@@

pedlist <<- seq(-12,30,6)
allp <- matrix(0,nrow=4,ncol=7)
allparams <- array(0,dim=c(4,ntotalsimplexfits,8))
allrms <- NULL
 for (cond in 1:3){
   print(cond)
   datatofit <<- meanthresh[cond,,]

@@

   finalout <- matrix(0,nrow=ntotalsimplexfits,ncol=8)
   for (n in 1:ntotalsimplexfits){
     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){
       load(file=paste0('local/fits/E',cond,'f',n,'.RData'))
       finalout[n,] <- allout
     }
   }
   i <- which(finalout[,1]==min(finalout[,1]))
   p <- 10^finalout[i[1],2:8]
   allrms[cond] <- finalout[i[1],1]
   p[2] <- p[2] + 1
   p[2] <- min(p[2],16)
   p[1] <- 1 + p[1] + p[2]
   p[1] <- min(p[1],20)
   p[3] <- 1 + p[3]
   allp[cond,] <- p
   allparams[cond,,] <- finalout

   pedlist <<- seq(-6,36,6)  # increase pedestal contrasts for the chromatic conditions

# finally fit the disc data
pedlist <<- seq(-12,30,6)
cond <- 4

   print(cond)
   datatofit <<- meanthresh3

   finalout <- matrix(0,nrow=ntotalsimplexfits,ncol=8)
   for (n in 1:ntotalsimplexfits){
     if (file.exists(paste0('local/fits/E',cond,'f',n,'.RData'))){
       load(file=paste0('local/fits/E',cond,'f',n,'.RData'))
       finalout[n,] <- allout
     }
   }
   i <- which(finalout[,1]==min(finalout[,1]))
   p <- 10^finalout[i[1],2:8]
   allrms[cond] <- finalout[i[1],1]
   p[2] <- p[2] + 1
   p[2] <- min(p[2],16)
   p[1] <- 1 + p[1] + p[2]
   p[1] <- min(p[1],20)
   p[3] <- 1 + p[3]
   allp[cond,] <- p
   allparams[cond,,] <- finalout

@@

```{r plotdippers, include=FALSE}

@@

pedlist <- -12:39
pedlevelsC <- 10^(pedlist/20)
pedlevelsC[1] <- 0
allpred <- array(0,dim=c(4,4,length(pedlist)))

for (expt in 1:4){
  for (cond in 1:4){
    for (pedlev in 1:length(pedlist)){
      allpred[expt,cond,pedlev] <- discriminate(allp[expt,],pedlevelsC[pedlev],cond)
    }
  }
}
allpreddB <- 20*log10(allpred)

pdf('Figures/dipperssimplex.pdf',width=12,height=10)

@@

ticklocsx <- seq(-12,36,6)
ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
ticklocsy <- seq(-12,36,6)
ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
pedcontrasts <- seq(-12,30,6)

exptorder <- c(1,3,2)
paneltitles <- c('(a) Achromatic thresholds','(b) Red/Green thresholds','(c) Blue/Yellow thresholds')
par(mfrow=c(2,3))
for (expt in 1:3){
par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main=paneltitles[expt],cex.main=2.5)

for (cond in 1:4){
  arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]+SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]-SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
  lines(pedlist,allpreddB[exptorder[expt],cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanthresh[exptorder[expt],cond,],pch=16,col=collist[cond],cex=1.5)
}
text(24,-9,paste0('RMSE = ',round(allrms[expt],digits=2),'dB'),cex=2)
if (expt==1){legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}

pedcontrasts <- c(-12,seq(0,36,6))  # update pedestal contrasts for plotting chromatic conditions

paneltitles <- c('(d) Achromatic slopes','(e) Red/Green slopes','(f) Blue/Yellow slopes')

ticklocsy <- seq(-6,18,6)
ticklabelsy <- c(0.5,1,2,4,8)

for (expt in 1:3){

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main=paneltitles[expt],cex.main=2.5)

for (cond in 1:4){
  arrows(pedcontrasts,meanslope[expt,cond,],pedcontrasts,meanslope[expt,cond,]+SEslope[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanslope[expt,cond,],pedcontrasts,meanslope[expt,cond,]-SEslope[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
  lines(pedcontrasts,meanslope[expt,cond,],col=collist[cond],lwd=2)
  # lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanslope[expt,cond,],pch=16,col=collist[cond],cex=1.5)
}

pdf('Figures/discdata.pdf',width=13,height=7)

par(mfcol=c(1,2))
pedcontrasts <- seq(-12,30,6)

ticklocsy <- seq(-18,30,6)
ticklabelsy <- c(0.125,0.25,0.5,1,2,4,8,16,32)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-18,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(a) Flickering disc (thresholds)',cex.main=2)

for (cond in 1:4){
  arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]+SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]-SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
  lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanthresh3[cond,],pch=16,col=collist[cond],cex=1.5)
}
text(24,-15,paste0('RMSE = ',round(allrms[4],digits=2),'dB'),cex=2)
legend(-12,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)

ticklocsy <- seq(-6,18,6)
ticklabelsy <- c(0.5,1,2,4,8)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(b) Flickering disc (slopes)',cex.main=2)

for (cond in 1:4){
  arrows(pedcontrasts,meanslope3[cond,],pedcontrasts,meanslope3[cond,]+SEslope3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanslope3[cond,],pedcontrasts,meanslope3[cond,]-SEslope3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
  lines(pedcontrasts,meanslope3[cond,],col=collist[cond],lwd=2)
  # lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanslope3[cond,],pch=16,col=collist[cond],cex=1.5)
}

@@

summation <- meanthresh[,1,1] - meanthresh[,2,1]
summationDisc <- meanthresh3[1,1] - meanthresh3[2,1]

@@

```{r domodellingstan, include=FALSE}

@@

modelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;  
  }
  parameters {
    vector<lower=0.1, upper=3>[Ndatasets] p;
    vector<lower=2, upper=8>[Ndatasets] q;
    vector<lower=1, upper=2>[Ndatasets] m;
    vector<lower=0.001, upper=2>[Ndatasets] S;  
    vector<lower=0.001, upper=1>[Ndatasets] Z;
    vector<lower=0.001,upper=2>[Ndatasets] w;
    vector<lower=0.001,upper=1>[Ndatasets] k;

    real<lower=0> sigma ;
    real<lower=0.1> pmu ; 
    real<lower=2> qmu ; 
    real<lower=1> mmu ;
    real<lower=0.001> Smu ;
    real<lower=0.001, upper=1> Zmu ; 
    real<lower=0.001> wmu ; 
    real<lower=0.001> kmu ;

@@

    pmu ~ normal( 1.4 , 0.1 ) ;
    qmu ~ normal( 6.59 , 0.5 ) ;
    mmu ~ normal( 1.28 , 0.2 ) ;
    Smu ~ normal( 0.985 , 0.2 ) ;
    Zmu ~ normal( 0.1 , 0.5 ) ;
    wmu ~ normal( 1 , 0.2 ) ;
    kmu ~ normal( 0.194 , 0.1 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    msigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Ssigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

@@

    dprime = (targresp-nullresp)/k[s[i]] ;
    if (is_nan(dprime)){
       dprime = 0;
    }
    if (is_inf(dprime)){
       dprime = 10;
    }
    if (dprime > 10){
       dprime = 10;
    }    
    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
    }
  }  
" # close quote for modelString

@@

ex1data <- read.csv('local/Experiment1.csv')
ex1data$Condition <- ceiling(ex1data$Condition/2)
ex3data <- read.csv('local/Experiment3.csv')
ex3data$Condition <- ceiling(ex3data$Condition/2)

@@

sublist3 <- unique(ex3data$Subject)
for (s in 1:length(sublist3)){
    datasetcounter <- datasetcounter + 1
    for (cond in 1:4){
      thisdipper <- subset(ex3data,Subject==sublist3[s] & Condition==cond)

      for (p in 1:length(pedconts)){
        thisthresh <- subset(thisdipper,PedestalContrast==pedconts[p])
        targconts <- sort(unique(thisthresh$TargetContrast))
        for (t in 1:length(targconts)){
          counter <- counter + 1
          thislevel <- subset(thisthresh,TargetContrast==targconts[t])
          ntrials[counter] <- nrow(thislevel)
          ncorrect[counter] <- sum(thislevel$IsCorrect)
          subjects[counter] <- s
          experiments[counter] <- 4
          datasets[counter] <- datasetcounter
          conditions[counter] <- cond
          pedestals[counter] <- pedconts[p]
          targets[counter] <- targconts[t]
        }
      }
    }
}

expdata <- data.frame(datasets,experiments,subjects,conditions,pedestals,targets,ntrials,ncorrect)

for (expt in 1:4){

thisexpt <- subset(expdata, experiments==expt)

dataList = list(ncorrect = thisexpt$ncorrect, ntrials = thisexpt$ntrials, PedestalContrast = thisexpt$pedestals, TargetContrast = thisexpt$targets, c = thisexpt$conditions, s = thisexpt$subjects, Ndatasets = length(unique(thisexpt$subjects)), Ntotal = nrow(thisexpt))

@@

save(file=paste0('local/stanfit',expt,'.RData'),list=c('stanFit'))

@@

allstanparams <- matrix(0,nrow=4,ncol=7)

load(paste0('local/stanfit1.RData'))
draws <- extract(stanFit)
p <- draws$pmu
allsamples <- array(0,dim=c(4,7,length(p)))

for (expt in 1:4){
  load(paste0('local/stanfit',expt,'.RData'))
  draws <- extract(stanFit)
  p <- mean(draws$pmu+draws$qmu)
  q <- mean(draws$qmu)
  m <- mean(draws$mmu)
  k <- mean(draws$kmu)
  S <- mean(draws$Smu)
  Z <- mean(draws$Zmu)
  w <- mean(draws$wmu)
  allstanparams[expt,] <- c(p,q,m,S,Z,w,k)

  allsamples[expt,1,] <- plist
  allsamples[expt,2,] <- qlist
  allsamples[expt,3,] <- mlist
  allsamples[expt,4,] <- Slist
  allsamples[expt,5,] <- Zlist
  allsamples[expt,6,] <- wlist
  allsamples[expt,7,] <- klist
}

@@

nrandomdraws <- 200

load('local/thresholddata.RData')
load('local/thresholddataDisc.RData')

threshtoplot <- array(0,dim=c(4,4,8))
threshtoplot[1:3,,] <- meanthresh
threshtoplot[4,,] <- meanthresh3

  pdf(paste0('Figures/stanoutput.pdf'),width=8,height=8)

  layout(matrix(c(1,1,2,2,3,3,4,4,1,1,2,2,3,3,4,4,8,8,8,9,9,9,5,5,8,8,8,9,9,9,5,5,8,8,8,9,9,9,6,6,10,10,10,11,11,11,6,6,10,10,10,11,11,11,7,7,10,10,10,11,11,11,7,7),8,8,byrow=TRUE))
  par(mar=c(3,2,1,1))
